Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-05 Grassmannian_cells.tex
Section 2 edits

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Covering Theory}

For an introduction to covering theory we refer to \cite{gab}.
Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.

Recall that every tuple of linear maps $(g_\alpha:X_{s(\alpha)}\to Y_{t(\alpha)})_{\alpha\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_i=X_i\oplus Y_i$ for all $i\in Q_0$ and linear maps $Z_\alpha=\begin{pmatrix}Y_\alpha &g_\alpha\\0&X_\alpha\end{pmatrix}$ for all $\alpha\in Q_1$. 
In general, considering the linear map  
\[d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_k(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_k(X_{s(\alpha)},Y_{t(\alpha)}), (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1} \]
we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.

Let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.  
\begin{definition}
  The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$, where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.

  The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$, where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.

  We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp. $\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp. $\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp. $G_Q \tilde X=X$), where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp. $G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
\end{definition}

Note that in our definition every covering quiver has infinitely many connected components.
But every connected component is a covering in the sense of \cite{gab}.
As indecomposable representations live on one component this makes no difference.
Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
In addition, observe that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.

\begin{lemma}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\tilde Q$.
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)$ of $\hat Q$ (resp. $(i,w)$ of $\tilde Q$).
  This gives the claim.
\end{proof}

The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
The group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
We say two representation (resp. dimension vectors) are equivalent in this case.
The analogous observation can also be made for $\tilde Q$.
If $M$ is a representation of $\hat Q$ (resp. $\tilde Q$), we denote the representation obtained by translation by $\chi\in A_Q$ (resp. $w\in W_Q$) by $M_\chi$ (resp. $M_w$).

As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
\begin{theorem}
  \label{covering}
  The functors $F_Q$ and $G_Q$ preserve indecomposability.
  Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
  \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
  The analogous statements are true when replacing $\Hom$ by $\Ext$ or $\Rep(\hat Q)$ by $\Rep(\tilde Q)$.
\end{theorem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Representation Theory of $K(n)$}

Fix $n\ge3$. Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
The category $\rep K(n)$ of finite-dimensional representations of $K(n)$ is equivalent to the category of modules over the path algebra $A(n)$ of $K(n)$.
As a $\CC$-vector space, the path algebra $A(n)$ can be written as $A_0\oplus A_1$, where 
\begin{itemize}
  \item $A_0=\CC e_1\oplus \CC e_2$ is a two-dimensional semisimple algebra with orthogonal idempotents $e_1$ and $e_2$;
  \item $A_1=\bigoplus_{i=1}^n \CC a_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, that is $e_ka_ie_\ell=\delta_{k1}\delta_{\ell2}a_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
\end{itemize}

@@

\begin{lemma}\label{le:homdecomposition}\sayT{I split up some lemmas. Check references}
Let $m\geq 2$. The following holds:
\begin{enumerate}
\item We have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional. 
\item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
      \begin{align}\label{ses1}\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\end{align}
  \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0.$$

\end{enumerate}
\end{lemma}
\begin{proof}
The first part is a consequence of Theorem \ref{covering}. Now the observations of Section \ref{sec:truncated preprojectives} immediately yield the second part. The last part is also a consequence of Theorem \ref{covering} as, for $1\leq i\neq k\leq n$, we have 
$$\kk= \Hom_{\tilde Q}(\tilde P_{m,k},\tilde P_{m,k})\cong \Hom_Q(P_{m},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})$$
which implies $\Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})=0$ for $i\neq k$. Now $\Ext(\tilde P_{m,i},\tilde P_{m,k})=0$ follows in the same manner using that $P_m$ is exceptional.

@@

     We have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  for $k\neq j_i$ for $i=1,\ldots,l$. 
		\item We have $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$ and $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$. 
		\item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.

  \end{enumerate}
\end{lemma} 
\begin{proof}

@@

\begin{lemma}
  \begin{enumerate}
    \item $\tilde P_m^{(i_1,\ldots,i_{n-1})}\cong\tilde P_{m-1}^{(i_n)}$
    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows for instance by induction when applying BGP-reflections.
\end{proof}
----TO HERE----DO NOT NEED THIS----
\end{comment}

@@

  The following holds:
  \begin{enumerate}
    \item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}=\tilde P_{m-2}^{(j_1,\ldots,j_l)}$.
    %\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$. What do we need? We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
    \item There exists a short exact sequences 
      \begin{align}\label{ses3}\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}\end{align}
      where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
    \item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.

@@

If $m=3$, we replace the short exact sequence (\ref{ses3}) by
 \begin{align}\label{ses4}\xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)\ar[r] & 0}.\end{align}
 Recall that the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is just $\tau'\tilde P_3^{\uj}:=\left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)$, see also Example \ref{smallm}.

@@

Fix a vector space $X$ of dimension $n$ and let $d\leq n$. We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$. Then we generalize the concept to quiver Grassmannians, but we will see that the torus fixed point set can be calculated in an analogous manner. Thus assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$. We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ which is compatible with this decomposition, i.e. there exist numbers $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
\[v_1,\ldots,v_{j_1}\in X_1,\,v_{j_1+1},\ldots,v_{j_2}\in X_2,\ldots,v_{j_{l-1}+1},\ldots,v_{n}\in X_l\]
Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$. Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(j)}v_i$ if $v_i\in X_j$ linearly to $X$. This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_d(X)$. We can write every $U\in\Gr_d(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e. there exists a unique sequence $1\leq i_1\leq\ldots\leq i_d\leq n$ and a unique matrix representation of $U$ of the form
\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{d,n}(k)\]
where the unit vectors are in the columns $i_1,\ldots,i_d$. All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_d)$. The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e. we have
\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}.\]
Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
\begin{lemma}\label{usualGrass}
Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$, $v_{i'}\in X_{j'}$ and $j\neq j'$.
Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.
\end{lemma}
\begin{proof}If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_i+1)}(U\cap X_i)=U\]
where $j_0=0$.

@@

%Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
\begin{proposition} \label{indecomposables}
  \sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
  \sayT{moved}  Let $m\geq 1$ and $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$. The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.

\end{proposition}
\begin{proof}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Covering Theory}

For an introduction to covering theory we refer to \cite{gab}.
Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:s(\alpha)\to t(\alpha)$.
A $\CC$-representation $X$ of $Q$ consists of a collection of $\CC$-vector spaces $X_i$ for $i\in Q_0$ and a collection of $\CC$-linear maps $X_\alpha:X_{s(\alpha)}\to X_{t(\alpha)}$ for $\alpha\in Q_1$.
Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
Write $\Rep(Q)$ for the abelian category of $\C$-representations of $Q$.

Recall that, given $\CC$-representations $X$ and $Y$ of $Q$, any tuple of linear maps $(g_\alpha:X_{s(\alpha)}\to Y_{t(\alpha)})_{\alpha\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term given by the vector spaces $Z_i=X_i\oplus Y_i$ for $i\in Q_0$ and the linear maps $Z_\alpha=\begin{pmatrix} X_\alpha & 0 \\ g_\alpha & Y_\alpha \end{pmatrix}$ for $\alpha\in Q_1$. 
In general, considering the linear map  
\[d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_\CC(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_\CC(X_{s(\alpha)},Y_{t(\alpha)}),\qquad (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1} \]
we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.

Let $W_Q$ be the free non-abelian group generated by $Q_1$.  
Write $A_Q\cong \ZZ^{Q_1}$ for the free abelian group generated by $Q_1$ and denote by $e_\alpha\in A_Q$ the generator corresponding to $\alpha\in Q_1$. 
\begin{definition}
  The \emph{universal abelian covering quiver} $\hat Q$ of $Q$ has vertices $\hat Q_0=Q_0\times A_Q$ and arrows $\hat Q_1=Q_1\times A_Q$, where $(\alpha,\chi):\big(s(\alpha),\chi\big)\to\big(t(\alpha),\chi+e_\alpha\big)$ for $\alpha\in Q_1$ and $\chi\in A_Q$.
  Write $F_Q:\Rep(\hat Q)\to\Rep(Q)$ for the natural functor.

  The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$ for $\alpha\in Q_1$ and $w\in W_Q$.
  Write $G_Q:\Rep(\widetilde Q)\to\Rep(Q)$ for the natural functor.

  We say that a representation $X\in\Rep(Q)$ can be \emph{lifted} to $\hat Q$ (resp. $\widetilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp. $\widetilde X\in\Rep(\widetilde Q)$) such that $F_Q\hat X=X$ (resp. $G_Q \widetilde X=X$).
\end{definition}

Note that in our definition every covering quiver has infinitely many connected components, but each of its connected components is a covering in the sense of \cite{gab}.
As indecomposable representations live on one of these components this distinction will be irrelevant.
Note that the natural surjection $W_Q\onto A_Q$ induces a functor $H_Q:\Rep(\widetilde Q)\to\Rep(\hat Q)$.
In addition, observe that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.

\begin{lemma}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\widetilde Q$.
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)$ of $\hat Q$ (resp. $(i,w)$ of $\widetilde Q$).
  This gives the claim.
\end{proof}

The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
We say that a dimension vector $\hat \bfe$ of $\hat Q$ is \emph{compatible} with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
The group $A_Q$ acts on $\hat Q$ via translation, this induces actions of $A_Q$ on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
We say two representation (resp. dimension vectors) are \emph{equivalent} if they can be related by the action of $A_Q$.
The analogous observation can also be made for $\widetilde Q$.
If $M$ is a representation of $\hat Q$ (resp. $\widetilde Q$), we denote by $M_\chi$ (resp. $M_w$) the representation obtained via translation by $\chi\in A_Q$ (resp. $w\in W_Q$).

As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain the following result from \cite{gab}.
\sayD{Citation needed?}
\begin{theorem}
  \label{covering}
  The functors $F_Q$ and $G_Q$ preserve indecomposability.
  Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
  \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X,\hat Y_\chi).\]
  Analogous isomorphisms exist when replacing $\Hom$ by $\Ext$ or $\Rep(\hat Q)$ by $\Rep(\widetilde Q)$.
\end{theorem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Representation Theory of $K(n)$}

Fix $n\ge3$. Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
The category $\rep K(n)$ of finite-dimensional representations of $K(n)$ is equivalent to the category of modules over the path algebra $A(n)$ of $K(n)$.
As a $\CC$-vector space, the path algebra $A(n)$ can be written as $A_0\oplus A_1$, where 
\begin{itemize}
  \item $A_0=\CC e_1\oplus \CC e_2$ is a two-dimensional semisimple algebra with orthogonal idempotents $e_1$ and $e_2$;
  \item $A_1=\bigoplus_{i=1}^n \CC\alpha_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, that is $e_k\alpha_ie_\ell=\delta_{k1}\delta_{\ell2}\alpha_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
\end{itemize}

@@

\begin{lemma}\label{le:homdecomposition}\sayT{I split up some lemmas. Check references}
Let $m\geq 2$. The following holds:
\begin{enumerate}
  \item We have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional. 
  \item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
      \begin{align}
        \label{ses1}
        \ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.
      \end{align}
  \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0.$$
\end{enumerate}
\end{lemma}
\begin{proof}
The first part is a consequence of Theorem \ref{covering}. Now the observations of Section \ref{sec:truncated preprojectives} immediately yield the second part. The last part is also a consequence of Theorem \ref{covering} as, for $1\leq i\neq k\leq n$, we have 
$$\kk= \Hom_{\tilde Q}(\tilde P_{m,k},\tilde P_{m,k})\cong \Hom_Q(P_{m},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})$$
which implies $\Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})=0$ for $i\neq k$. Now $\Ext(\tilde P_{m,i},\tilde P_{m,k})=0$ follows in the same manner using that $P_m$ is exceptional.

@@

      We have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  for $k\neq j_i$ for $i=1,\ldots,l$. 
    \item We have $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$ and $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$. 
    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
  \end{enumerate}
\end{lemma} 
\begin{proof}

@@

\begin{lemma}
  \begin{enumerate}
    \item $\tilde P_m^{(i_1,\ldots,i_{n-1})}\cong\tilde P_{m-1}^{(i_n)}$
    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)}),\]
      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows for instance by induction when applying BGP-reflections.
\end{proof}
----TO HERE----DO NOT NEED THIS----
\end{comment}

@@

  The following holds:
  \begin{enumerate}
    \item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}=\tilde P_{m-2}^{(j_1,\ldots,j_l)}$.
    %\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$. What do we need? We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
    \item There exists a short exact sequences 
      \begin{align}
        \label{ses3}
        \sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}
      \end{align}
      where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
    \item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.

@@

If $m=3$, we replace the short exact sequence (\ref{ses3}) by
 \begin{align}
   \label{ses4}
   \xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)\ar[r] & 0}.
 \end{align}
 Recall that the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is just $\tau'\tilde P_3^{\uj}:=\left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)$, see also Example \ref{smallm}.

@@

Fix a vector space $X$ of dimension $n$ and let $d\leq n$. We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$. Then we generalize the concept to quiver Grassmannians, but we will see that the torus fixed point set can be calculated in an analogous manner. Thus assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$. We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ which is compatible with this decomposition, i.e. there exist numbers $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
\[v_1,\ldots,v_{j_1}\in X_1,\,v_{j_1+1},\ldots,v_{j_2}\in X_2,\ldots,v_{j_{l-1}+1},\ldots,v_{n}\in X_l\]
Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$. Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(j)}v_i$ if $v_i\in X_j$ linearly to $X$. This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_d(X)$. We can write every $U\in\Gr_d(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e. there exists a unique sequence $1\leq i_1\leq\ldots\leq i_d\leq n$ and a unique matrix representation of $U$ of the form
\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{d,n}(k)\]
where the unit vectors are in the columns $i_1,\ldots,i_d$. All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_d)$. The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e. we have
\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}.\]
Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
\begin{lemma}
  \label{usualGrass}
  Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$, $v_{i'}\in X_{j'}$ and $j\neq j'$.
  Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.
\end{lemma}
\begin{proof}
  If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_i+1)}(U\cap X_i)=U\]
where $j_0=0$.

@@

%Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
\begin{proposition} \label{indecomposables}
  Let $m\geq 1$ and $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$. The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
\end{proposition}
\begin{proof}
